\chapter{Introduction}

This chapter presents the background, objectives, and work plan of
the report, as required by the regulations for the final-year
project of the Faculty of Computer Science
(\href{https://informatica.ucm.es/normativa-tfm-2425}{informatica.ucm.es/normativa-tfm-2425}).

\section{Regulations}

\begin{itemize}\setlength{\itemsep}{0pt}
  \item Minimum length: 25 pages for a single-author Bachelor's
        thesis (plus 5 per additional co-author); 50 pages for a
        Master's thesis.
  \item At most 10 keywords in each language.
  \item The English abstract of the Master's thesis must be
        approximately half a page long.
  \item All non-original material (text, figures, code) must be
        cited and respect its license.
  \item \textbf{Master's thesis only}: the student must sign and
        attach the \emph{responsible declaration on authorship and
        ethical use of artificial intelligence tools}.
\end{itemize}

\section{Background}

The Faculty of Computer Science at UCM has used the TeXiS~\cite{texis}
system for over a decade for its thesis reports and final-year
projects. This shell helps prepare complex documents with good
practices, but being a shell rather than a template, it is more
difficult to integrate with other systems, and it does not
encourage users to learn LaTeX.

\section{Objectives}

The objectives of this work are:
\begin{itemize}
  \item Provide a modern template based on LuaLaTeX.
  \item Separate normative aspects from aesthetic ones.
  \item Offer a minimal base that does not interfere with the
        packages each student chooses to use.
\end{itemize}
